\documentclass[11pt]{article}
\usepackage{geometry,url, hyperref}
\geometry{margin=1in, centering}
%\pagestyle{empty}
\usepackage[utf8]{inputenc}
\usepackage{multicol, multirow}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw, color, soul, booktabs, graphicx}
\usepackage{caption}
\usepackage{lmodern}
\usepackage[T1]{fontenc}  % Ensure proper encoding
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\large\bfseries\sffamily}{\thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\normalsize\bfseries\sffamily}{\thesection}{1em}{}
  
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    citecolor=blue,
}

\pagenumbering{arabic}

\begin{document}

\fontfamily{lmss}\selectfont

\begin{center}
  \textbf{\huge EC 380: International Economic Issues}\\ 
  \vspace{0.1in}
  Winter 2025
\end{center}

\bigskip

Welcome!
I'm very happy to have you on board. 
I don't expect this GE assignment to be much more demanding the average one.

\section*{Responsibilities Overview}

\input{Responsibilities}

\section*{Expectations}
I only ask three things:

\begin{itemize}
  \item That grading takes at most 1 week after the due date to be completed
  \item That you provide some form of feedback in your grading.
  At the very minimum a +/- points gained/lost for each graded question.
  They will be given answer keys for each assignment.
  \item I understand you are also very busy with your own work, so please let me know if anything ever comes up. 
  I aim to be understanding and believe that communication is crucial!
\end{itemize} 

%\section*{In-Class Activity}
%Starting in Week 2, every other week I will be conducting an in-class activity in which I will be needing your presence, mainly as an extra set of hands.
%It will be toward the last 30min of the class so hopefully there's no overlap with your own field courses.
%If there are any issues, let me know! 
%Your own classes should be your priority. 

%The in-class activity is essentially a self-run world market where students are in groups and behave as producing/exporting nations. 
%They will be given materials (paper, scissors, rulers, etc.) and they have to create shapes that they then have to ``sell" to a buyer (us). 
%Your responsibilities here will be to help me keep eyes on the class and be ``quality assurance" for the shapes they produce. 

%Beyond being in-person, I might ask you to digitize the collected data from the activity. 
%It would just be some quick data entry into an excel sheet. 
%If it ends up being simple, I'll do it myself. 

\section*{Grading}
There will be 5 Problem Sets, a Midterm Exam, and a Final Exam.
You will be responsible for grading all of these. 
I will give you an answer key to grade off and further instructions for each problem set (some might only ask you to grade some questions in detail and others for completion, for example). 

The exams will be straightforward grading responsibilities. 
The only quirk is that I'll give you an excel sheet to keep track of question performance for me. 
It's how I keep control of which questions may be unclear or too difficult. 
I hope it's simple to follow but I'll provide more details as we get closer to it happening. 

Submissions will be digital on Canvas. 
I've made it so they can only submit pdfs which should normalize submissions. 
I'll go through an example of how to make a pdf and all those details with them, so any deviation from this should result in a penalty for them. 
I'll be clear in my instructions. 

I do my best to let the students know that I am who they should contact in case of any grading issues, but they get around me sometimes. 
If you are ever contacted directly, use common sense with smaller issues. 
If it is something more significant, or something you do not know how to navigate, let me know and I'll deal with it. 

There are Quizzes on Canvas but I will grade those. 

\subsection*{Late Submissions}
I will set up Canvas to automatically penalize late submissions.
So if there is a late submission, grade it as you would normally and Canvas will deal with the point reduction. 

\newpage

%\input{Term-Schedule}

%\restoregeometry

%\vspace*{.15in}
%\section*\textbf{GRADING BREAKDOWN} 
%\begin{center} \begin{minipage}{3.8in}\begin{flushleft}
    %\hyperlink{Exam_Rubric}{Exams} \dotfill 70\% \\
    %\hyperlink{HW_Rubric}{Achieve Homework} \dotfill 10\% \\
    %\hyperlink{HW_Rubric}{ Quiz} \dotfill 20\%
%\end{flushleft}\end{minipage}\end{center}

\end{document}