\documentclass[12pt]{exam}
\usepackage{amsthm}
\usepackage{libertine}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{multicol}
\usepackage[shortlabels]{enumitem}
\usepackage{siunitx}
\usepackage{cancel}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{tikz}
\usepackage[T1]{fontenc}  % Ensure proper encoding
\usepackage{titlesec}
\usepackage{booktabs}

\CorrectChoiceEmphasis{\color{red}\bfseries\itshape}

\newcommand{\class}{\fontfamily{lmss} \textbf{EC 380}} % This is the name of the course 
\newcommand{\examnum}{\fontfamily{lmss} \textbf{PS 01}} % This is the name of the assignment
\newcommand{\examdate}{\fontfamily{lmss} \textbf{January 15 at 01:59pm}} % This is the due date
\newcommand{\timelimit}{}
\addpoints % Allows to add points up to include table at end of document

\pagestyle{headandfoot} % Fancy equivalent for exam documentclass
\firstpageheadrule % Horizontal bar in first page
\runningheadrule % Horizontal bar in rest of pages
\firstpageheader{\class}{\examnum}{\fontfamily{lmss} Due \examdate} % 1st page header content
\firstpagefooter{\fontfamily{lmss} Points earned: \makebox[1in]{\hrulefill} / \pointsonpage{\thepage} points}{}{\thepage\ of \numpages} % 1st page footer content
\runningheader{\class}{\examnum}{\fontfamily{lmss} Due \examdate} % Rest of pages header content
\runningfooter{\fontfamily{lmss} Points earned: \makebox[1in]{\hrulefill} / \pointsonpage{\thepage} points}{}{\thepage\ of \numpages} % Rest of pages footer content
\bracketedpoints % Puts points per question inside brackets instead of parenthesis 

\titleformat{\section}
  {\normalfont\large\bfseries\sffamily}{\thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\normalsize\bfseries\sffamily}{\thesection}{1em}{}

\begin{document}
\fontfamily{lmss}
\selectfont

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
    \textbf{{\LARGE EC 380 Problem Set 01}} \\
    \bigskip 
\end{center}

\noindent \textbf{Instructions:} 
Answers must be submitted online through the designated Canvas assignment in a \textbf{PDF file}.
Any other file type is not allowed. 
This Problem Set is due on \examdate.
Please write as legible and clearly as possible. 
You will not be given full credit if your answers cannot be easily understood. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% QUESTIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Questions}
\begin{questions}

\question
Answer the following short questions:

\begin{parts}
    \part[5] How is the Trade to GDP ratio measured?
    \vspace*{\stretch{1}}
    \part[10] Have trade frictions \textbf{increased or decreased} over time? How has this \textbf{increase/decrease} impacted trade flows? 
    \vspace*{\stretch{1}}
    \part[5] One possible explanation for increased trade is given by the Krugman model, which says \textbf{Demand for variety of goods motivates trade}.
    How does wanting different type of goods motivate international trade?
    \footnote{We will not be covering this model in depth, but you should arrive at a logical answer given the model's main result}.
    \vspace*{\stretch{1}}
\end{parts} 

\newpage 

\question
Suppose we are considering a \textbf{Ricardian Model} setting, where countries have not yet opened up to trade. 
Two goods are produced exclusively by domestic labor supplies, Rubber Ducks and Bath Bombs. 
Home and foreign produce both goods as in the table below. 
The two countries have a labor pool $\bar{L} = 30$ each, which means there is no difference in their labor endowments. 

\input{tables/Q2-table}

Consider the autarky scenario where neither country exchange goods. 
Complete the following questions to obtain the two countries consumption and production equilibria. 

\begin{parts}
    \part[4] Which country has \textbf{comparative advantage in producing Bath Bombs}?
    \vspace*{2in}
    \part[4] What is the \textbf{price of Rubber Ducks} in each country?
    \vspace*{2in}
    \part[4] What are the \textbf{maximum quantities of each good} that Home and Foreign can produce? (Fill in the table) 
    \vspace*{0.3in}
    \input{tables/Q2-table-b}
    \newpage
    \part[8] Sketch the PPFs for \textbf{both countries} in a single graph. 
    Be sure to correctly label the graph for full credit. 
    \vspace*{\stretch{2}}
    \part[2] What should be the \textbf{World Price of Rubber Ducks}?  
    \vspace*{\stretch{1}}
    \part[8] Suppose Home prefers to consume \textbf{5 Rubber Ducks} for every \textbf{2 Bath Bombs}. 
    Calculate the consumption bundle of Home. 
    \vspace*{\stretch{2}}

\end{parts}    
\end{questions}
\end{document}
